---
title: "collect_ff"
---

#### Description

The `collect_ff` function collects fresh data from [fantasy.premierleague.com](http://fantasy.premierleague.com), it will take a while to complete and is to be used sparingly

#### Usage
```{r, eval=FALSE}
collect_ff(n = 600, specify_ids = NULL, .progress = "none")
```

#### Arguments

param | details
------|--------
n | the number of players (default = 600)
specify_ids | numeric vector, enter ids to collect data for specific players
.progress | progress bar (from plyr), options inc. "text", "time", "tk" or "win"

#### Details

Users can specify the number of players they wish to collect data for by changing the n parameter. If n is greater than the number of players, the function will only return the number of players available, however it will attempt to find n players, so do not input large n. The number of players in the game is around 550, the default value of n is 600.

Alternatively, passing a numeric vector to the specify_ids parameter, it is possible to collect data for specific players (I am unsure if ids change during the season). This function takes some time to run, and returns a list which can then be turned into dataframes using other functions in the package, see [players_df](players_df.html), [pastseasons_df](pastseasons_df.html).

#### Example use
```{r, eval=FALSE}
# collect players with ids 1 thru 50
new_list <- collect_ff(n = 50)

# collect players with ids 500 thru 550
new_list <- collect_ff(specify_ids = 500:550)
```