---
title: "season201415"
---

#### Description

The **season201415** dataset contains data for each of the gameweeks in the [fantasy.premierleague.com](http://fantasy.premierleague.com) game.  The data is player based, so each player in the game could have up to 38 rows of data (1 per gameweek) with variables such as points scored, gameweek value, net transters, etc.

Once the package has been installed and loaded, to access the dataset
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(fantasysocceR)
```

```{r}
data(season201415)
```

The dataset has `r dim(season201415)[1]` rows and `r dim(season201415)[2]` columns, its structure is:

```{r echo=FALSE}
str(season201415)
```

#### Example plot

The number of players per team to have played more than 80% of possible minutes, we'll use `dplyr` to manipulate the data and `ggplot2` to plot it, we'll also use the `team_pal` function included in the **fantasysocceR** package to style the plot:

```{r warning=FALSE, message=FALSE, fig.align='center'}
library(dplyr)
library(ggplot2)

season201415 %>% 
    group_by(id, name, team) %>% 
    summarise(total_mins = sum(mins)) %>% 
    ungroup() %>% 
    filter(total_mins > (0.8 * (90 * 38))) %>% 
    group_by(team) %>% 
    summarise(n_players = n()) %>% 
    ggplot(aes(x = team, y = n_players, fill = team)) + 
        geom_bar(stat = "identity") + 
        scale_fill_manual(values = team_pal(), guide=F) + 
        labs(x = "Team",
             y = "Players",
             title = "No. of players to play in >80% of possible minutes") +
        theme_minimal() + 
        theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1))
```