---
title: "team_pal"
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(fantasysocceR)
```

#### Description

The `team_pal` function provides a simple palette for the teams in the 2014/15 Premiership season.

#### Usage
```{r, eval=FALSE}
team_pal(teams = NULL, simple = TRUE, n = 1)
```

#### Arguments

param | details
------|--------
teams | which teams colours are required
simple | return a single colour per team
n | return more than a single colour (max of 3)

#### Example use

For most plots all that is needed is a single colour, these can be returned by simply calling the function and leaving the defaults as they are, which returns a named vector:

```{r}
team_pal()
```

If only a few teams are required, then enter the team names as a vector, and a named vector will be returned.

```{r}
team_pal(teams = c("Arsenal", "Man City", "Chelsea", "Man Utd"))
```

If more than one colour for a team is required, then enter a single team name and alter the `n` argument

```{r}
team_pal(team = "Arsenal", n = 3)
```
